---
# quarto::quarto_render("README.qmd", output_format = "all")
# quarto render README.qmd --to html,gfm
# quarto typst compile README.typ
title: pipeline for robotweath.com post
description: targets, webR and dashboard
format:
  dashboard:
    orientation: rows
    theme: default
    # expandable: true
    # scrolling: false
    nav-buttons:
     # - reddit
     - icon: gitlab
       href: https://gitlab.com/johngavin/robotweath.com
  # https://quarto.org/docs/output-formats/typst.html#overview
  # ~/Documents_/note_taking_atom/projects/rix/quarto_typst.md
  # Typst creates PDF output
  typst:
    keep-typ: false
    toc: true
    section-numbering: 1.1.a
    columns: 2
  html:
  # https://quarto.org/docs/computations/r.html#data-frames
  # https://quarto.org/docs/computations/r.html#output-formats
    # paging for row/col overflow
    # pages => add navbar in dashboard 
    # df-print: paged
    toc: true
    code-fold: true
    number-sections: true
    # css: styles.css
# output: github_document # /html_document # NB: OLD Rmarkdown
filters:
  - webr
webr:
  packages:
  # CRAN packages installed when page opened
  - "ggplot2"
  - "dplyr" # dplyr::`%>%`
  # - "tidyverse" # avoid to speed up pg load
  # - "tidygraph"
  # - "igraph"
  # - "ggdag"
execute:
  echo: false
  error: true
# embed-resources: true
editor: source
# Quarto with R => need rmarkdown => knitr engine
engine: knitr
knitr: 
  # also global Knitr options using opts_knit
  # https://quarto.org/docs/computations/r.html#knitr-options
  opts_chunk: 
    # https://yihui.org/knitr/options/
    collapse: true
    comment: "#>"
    # # https://quarto.org/docs/computations/execution-options.html#figure-options
    fig.path: "man/figures/README-"
    out.width: "100%"
    R.options:
      knitr.graphics.auto_pdf: true
# https://quarto.org/docs/computations/python.html
# jupyter: python3
#
# Quarto Publish publish.yml
# quarto::quarto_render("README.qmd", output_format = "all")
# quarto render README.qmd --to html,gfm,
# quarto typst compile README.typ
# 
# https://quarto.org/docs/publishing/github-pages.html
# quarto publish gh-pages README.qmd --no-prompt --to index.html 
---


<!-- README.md is generated from README.qmd. Please edit that file -->
<!---
  enclose ALL chunks with {webr-r} - not {r}
  then play each in webpage sequentially
  else {r} runs locally only
  ~/Documents_GitHub/ibrokers/vignettes/webr_dag_golem_owl.qmd
--->

```{r quarto cli, include = FALSE}
# https://quarto.org/docs/computations/r.html#chunk-options
# #| fig-cap: !expr 'paste("Air", "Quality")'
#| eval: false
#| collapse: true
#| label: quarto cli
#| echo: true
# system(" quarto preview README.qmd --to default ") # --no-watch-inputs --no-browse
# 
# NB: knitr::opts_chunk$set in yaml header above
# knitr::opts_chunk$set( # now in yaml above
#   collapse = TRUE, comment = "#>",
#   fig.path = "man/figures/README-",
#   out.width = "100%")
```


<!-- badges: start -->

<!-- badges: end -->

Some text
[in HTML.]{.content-visible when-format="html"}
[in PDF.]{.content-visible when-format="pdf"}

::: {.content-visible when-format="md"}
<!-- 
For README.md only (when-format="md")
See below (when-format="html") for  README.html
-->

# robotwealth.com

The goal of robotwealth.com is build a `{targets}` pipeline of a blog post from robotwealth.com.

-   [https://robotwealth.com/how-to-model-features-as-expected-returns/]

## expected return models

./R/robotwealth.com/expected_returns_models.R

-   features \~ expected returns
    -   objective
        -   predict then capitalise on future returns
    -   intuitive optimisation and implementation
    -   direct comparison of features
    -   framework to add/eval old/new signals
-   common *risk* models
    -   e.g. covariance estimates
-   expected return & risk models
    -   direct comparison with trading costs
    -   optimisation techniques to trade-off
        -   return, risk, and turnover given constraints

## Installation

Install the development version of robotwealth.com from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("JohnGavin/robotwealth.com")
```

## Project structure

### Tree structure

```{r tree}
#| code-fold: true
#| collapse: true
# output: asis
pacman::p_load(dplyr, stringr, fs)
excl <- "(figures)|(result)|(objects)|[.](md)|[.](htm)|[.](png)|(files)|(meta)|(old)"
incl <- "(A-Z)|(R)|(data)|(README)|[.](md)|[.](htm)|[.](yaml)|[.](yml)|[.](qmd)|[.](nix)|[.](R)"
incl %>% 
  fs::dir_tree(regexp = ., invert = F, recurse = F) %>% 
  head(20)
```

### File sizes

```{r dir_info}
"." %>% 
  dir_info(recurse = T) %>% 
  mutate(modify_date =
    as.Date(modification_time)) %>% 
  select(path, size, modify_date) %>% 
  filter(path %>% 
    str_detect(pattern = regex, negate = T)) %>% 
   arrange(desc(size))
```

## Pipeline example

### `targets::tar_make`

```{r tar_make}
#| echo: false
#| code-fold: true
#| collapse: true

# library(robotwealth.com)
pacman::p_load(targets)
# targets setup
scr <- "exp_ret_mdl.R"
str <- "exp_ret_mdl_store"
targets::tar_config_set(script = scr, store = str)
targets::tar_make(callr_function = NULL)  
```

### Print data

```{r perps_all}
tar_read(perps_all)
```

### Plot graphs

```{r gg_eq_curve_1}
# TODO: link each plot to 
# https://robotwealth.com/how-to-model-features-as-expected-returns/
#| label: gg_eq_curve_1 sdfsdf
#| fig-cap: "Equity curve 1/2)"
#| fig-alt: "Equity curve 1:"
#| echo: false
tar_read(gg_eq_curve_1)
```
```{r gg_eq_curve_2}
#| fig-cap: "Equity curve 2/2)"
#| fig-alt: "Equity curve 2:"
tar_read(gg_eq_curve_2)
```
```{r gg_trd_buf_param}
#| fig-cap: "Trade buffer parameter"
#| fig-alt: "Trade buffer parameter:"
tar_read(gg_trd_buf_param)
```
```{r gg_turnover}
#| fig-cap: "Trade buffer parameter"
#| fig-alt: "Trade buffer parameter:"
tar_read(gg_turnover)
```
```{r gg_orig_yes_cost}
#| fig-cap: "Orig with costs"
#| fig-alt: "Orig with costs."
tar_read(gg_orig_yes_cost)
```
```{r gg_returns_plot}
#| fig-cap: "Returns"
#| fig-alt: "Returns plot."
tar_read(gg_returns_plot)
```
```{r gg_weights_plot}
#| fig-cap: "weights"
#| fig-alt: "weights plot."
tar_read(gg_weights_plot)
```
```{r gg_rets_wghts}
#| fig-cap: "Returns and weights"
#| fig-alt: "weights plot."
tar_read(gg_rets_wghts)
```

```{r sessionInfo}
#| eval: true
#| collapse: true
#| label: sessionInfo
#| echo: true
# sessionInfo
# 
```

```{bash}
echo "foo" 
```

:::

::: {.content-visible when-format="html"}
<!-- 
For README.md only (when-format="html")
See below (when-format="md") for  README.html
-->



:::

# End

::: {.block fill="luma(230)" inset="8pt" radius="4pt"}

This is a block with gray background and slightly rounded corners.

https://quarto.org/docs/output-formats/typst.html#typst-blocks

:::
